---
title: "Topic"
subtitle: "FSH 507 Fall 2019"
author: "Your Name"
date: " `r Sys.Date()`"
output:
  ioslides_presentation: default
  powerpoint_presentation: default
  html_document: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(gganimate)
library(gapminder)
```

# R Markdown

## Getting Started

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown for presentations see <https://bookdown.org/yihui/rmarkdown/presentations.html>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


# Materials

## stuff

Tyler Clavelle and I wrote a data-wrangling intro several years ago so it might be a bit out of date, but you can take whatever you want from it

https://github.com/tclavelle/dplyr-tidyr-tutorial/blob/master/dplyr-tidyr-tutorial.Rmd

## Key things IMO:

* what is tidy data?

* key verbs and things
  - piping! 
  - select
  - filter
  - joins (left_, right_, full_)
  - group_by
  - mutate
  - summarise
  - gather
  - spread
  
## More things in the `tidyverse`

strings with `stringr`

dates with `lubridate`

factors with `forcats`
  
## ideas for exercise
  - tidy the FAO data (I've put it in the data folder)
  - For bonus, join it to the gapminder dataset (library(gapminder)), has development metrics by country and year
